A methodology for calculating active force-time functions from broadband piezoelectric sensors

### 2020-04-30 Article_file_Source_reconstruction.tex
Updates from Overleaf

\title{A methodology for calculating active source-time functions from broadband piezoelectric sensors in the laboratory}

@@

\begin{keyword}
Acoustic emissions, physical acoustics, non-destructive testing, active source methods
\end{keyword}
\end{frontmatter}

@@

Understanding wave elastodynamic waves propagate through a medium has proven to have a multitude of applications in many fields of science and engineering.  
\\

Application in material science (crack detection), biomedics (ultrasonics), \textbf{more?} 
\\
The premise is to use well-understood physics associated with wave propagation, in fluids or solids media, to probe properties and assess its state in a non-destructive manner.

\\\

The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies. To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources. We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.  By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty. We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.

\section{Experimental facilities}
\subsection{General}

@@

Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame. Small rummer pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame. Material properties of the steel plate required to model the wave propagation problem in the steel plate are given in Table \ref{table1}. Centrally located on the top surface is a piezoelectric actuator built in-house.  This sensor is connected to an high-voltage pulsing unit (HVP, Elsys Instruments AE-HV-MUX). This unit consist of a PiezosystemJena voltage amplifier for pulse generation (HVP 1000/200) that is fully integrated with the data acquisition (DAQ) software (Elsys Instruments TraNET). Figure \ref{fig1}(c) shows the circuit diagram of the HPV that is used to deliver an amplified voltage pulse to the piezoelectric actuator. The pulse and discharge of the system is depicted in the Figure \ref{fig1}(d). The time-dependent change in voltage when the switch position is in ``pulse'' (state 1) is given as:

@@

\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatic theory.  Figure \ref{fig1}(b) show the array holder for the passive sensor (KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source. The aluminium array had a 7 $\time$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.  In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e. aligned in the $3$-direction) and, therefore, have focused most of our sensors converge to one quadrant.  Similar colors of the sensors locations in Figure \ref{fig1}(b), represents similar epicentral locations.  We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and have shown that there appear to be little to no directivity in the active source.

@@

The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1988}. More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space. These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology. These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g. ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.). We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method. This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.

developing more understanding of realistic force-time function produced by the PZT actuators has many potential benefits. Due to these properties we are able simply study and isolate individual components of the ``toolchain''.

\begin{figure}[h]
     	\centering
\includegraphics[scale= 1.0]{FIG2.pdf} 
\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function. The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}. P and S waves are highlighted for reference only. The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
	\label{fig2} 
\end{figure}

@@

We build on the recent studies of signal analysis and instrument calibration by \citet{McLaksey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}. Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our system in a linear time-invariant (LTI) fashion. This assumes that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations of both the sensor and source location, which might be influenced so-called ``aperture'' effect. However, this is minimized by using the point contact conical PZT crystal, which will be discussed later when we examine in more detail how the force systems of passive and active PZT sensors.

@@

\subsection{Time domain characteristics of the Force Function}
\label{force_time}

@@

>>>>

\title{A methodology for calculating active force-time functions from broadband piezoelectric sensors}

@@

\begin{keyword}
Acoustic emissions,  piezoelectric sensors, absolute source calibration 
\end{keyword}
\end{frontmatter}

@@

Understanding the theory associated with elastodynamic wave propagation in materials has proven to be highly applicable to many disciplines in science and engineering. The general principle follows that by measuring the kinematic motion at a point in/on the media, perturbed by the incoming elastic waves, we can use wave propagation theory to back calculate critical information. The particle motions within the body are governed by the wave equation and the body itself can be solid or fluid materials and the waves carry both information of the media in which they propagate and of the source which caused them. This concept has made for many practical and highly interdisciplinary application. It has been widely applied in the fields of seismology, biomedicine, and nondestructive testing, to name a few.

The concept relies heavily on understanding attributes to three key components: (\textit{i}) source, (\textit{ii}) material and (\textit{iii}) receiver. In most applications, these waves are non-intrusive, propagating elastically through the medium from the source to receiver. From this, the problem benefits from \textit{source-receiver reciprocity} and due to symmetry of the wave equation, \textit{time invariance} applies, making this a versatile and flexible tool.

Sources can occur due to anthropogenic forcing, for example, rock samples subjected to outside stresses in a laboratory setting can crack locally, generating acoustic emissions \citep[e.g.][]{Lei2014}. These emission cause vibrations within sample using peizoelectric sensors in the laboratory. This phenomena also scales up to mining activities where microseismic studies are performed to ensure safety during engineering activities \citep[e.g.][]{Manthei2018}. Further up the scale, that large earthquakes occurring on faults in nature, occur naturally, activated by slow tectonic loading on geologic timescale. At each scale, the physic governing wave propagation holds and the vibrations through the medium are studied with arrays of sensors that are sensitive to vibrations at a range of frequencies. When the sources occur due to spontaneous instability, we consider this to be passive monitoring.

Sources can also be actively imposed, meaning that a transient force must manufactured within or on the body of interest. Since the wave equation still governs the resulting motions throughout the body, it becomes an important tool to study the material properties or changes them over time. Moreover, if multiple sources can be manufactured, understanding structures becomes possible through, for example, tomographic inversion.  This has been particularly important in the medical industry, where ultrasonic sensors can act as source or receivers and structures within the body can non-invasively be reconstructed through ultrasound computer tomography (USCT) \citep[e.g.][]Christensen1988}. While this methods assume that acoustic waves propagate (i.e. fluid), \textit{active field survey} in geophysics assume that the material is a solid and can reconstruct the subsurface to a high degree of certainty using `shot gather' approach and having well-constrained and repeatable sources.

In this study, we aim to study properties of ab active source produced in a controlled laboratory setting. Active survey in the laboratory have been employed for decades and typically study vibrations in the range of 100 kHz to 5 MHz. Many source can be manufactured from pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive \citep{Breckenridge1990}. As stated above, understanding attributes of the source is paramount to gaining more insight of the material it samples with the elastic waves. We aim to better understand the exact nature of the transient force produced when a rapid voltage transient is applied to a conical piezoelectric actuator. However, since direct measurement of this force is not easy at the frequencies required, we aim to infer the force-time function by studying the ground motions on an array of passive sensors. To simplify the problem we study the wave propagation problem in a homogeneous and elastic material.

The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1885}. More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space. These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology. These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g. ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.). We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method. This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.

\begin{figure}[h]
     	\centering
\includegraphics[scale= 1.0]{FIG2.pdf} 
\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function. The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}. P and S waves are highlighted for reference only. The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
	\label{fig2} 
\end{figure}
\section{Experimental facilities}
\subsection{General}

@@

Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame. Small rubber pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame. Material properties of the steel plate required to model the wave propagation problem in the steel plate are given in Table \ref{table1}. Centrally located on the top surface is a piezoelectric actuator built in-house.  This sensor is connected to an high-voltage pulsing unit (HVP, Elsys Instruments AE-HV-MUX). This unit consist of a PiezosystemJena voltage amplifier for pulse generation (HVP 1000/200) that is fully integrated with the data acquisition (DAQ) software (Elsys Instruments TraNET). Figure \ref{fig1}(c) shows the circuit diagram of the HPV that is used to deliver an amplified voltage pulse to the piezoelectric actuator. The pulse and discharge of the system is depicted in the Figure \ref{fig1}(d). The time-dependent change in voltage when the switch position is in ``pulse'' (state 1) is given as:

@@

\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatic theory.  Figure \ref{fig1}(b) show the array holder for the passive sensor (KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source. The aluminium array had a 7 $\times$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.  In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e. aligned in the $3$-direction) and, therefore, have focused most of our sensors converge to one quadrant.  Similar colors of the sensors locations in Figure \ref{fig1}(b), represents similar epicentral locations.  We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and have shown that there appear to be little to no directivity in the active source.

@@

@@

We build on the recent studies of signal analysis and instrument calibration by \citet{McLaskey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}. Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our system in a linear time-invariant (LTI) fashion. This assumes that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations of both the sensor and source location, which might be influenced so-called ``aperture'' effect. However, this is minimized by using the point contact conical PZT crystal, which will be discussed later when we examine in more detail how the force systems of passive and active PZT sensors.

@@

\subsection{Time Domain Characteristics of the Force-Time Function}
\label{force_time}

@@

\section{Discussion}

%The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies. To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources. We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.  By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty. We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
